Figures main manuscript

### 2020-03-27 code/05_figures-and-correlations.rmd
Made Fig 2 legend keys wider to distinguis between linetypes better

```{r Density-plot, fig.height=4, fig.width=6.47}
I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity)) + 
  geom_histogram(data = observed, aes(y = ..density.., x = I2, fill = Heterogeneity), bins = 100, alpha = 0.6)   +
  stat_density(geom="line", position="identity", #we use stat_density instead of geom_density to get only the density lines (and no fill)
               aes(linetype = Heterogeneity, color = Heterogeneity), size = 0.75)+ 
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
  scale_fill_manual(name = NULL, #drop legend title so that can place directly under other legend
                    values = "#666666", #fill color
                    breaks = "Observed",
                    labels = "Observed") +
  scale_color_manual(values = c("#D95F02", "#E6AB02", "#1B9E77","#E7298A"), #fill colors
                     breaks = c("Zero", "Small", "Medium", "Large"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
  theme(legend.position = c(0.85, 0.71), #placement of legend
        legend.spacing = unit(-0.4, "cm"), #move the two legends close to each other to seem like one
        legend.background = element_blank(), #remove legend background so that we can put a shared box around the two legends
        legend.box.background = element_rect(colour = "black")) + #create the shared box
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(I)^2," index", sep = ""))) +
  guides(linetype = guide_legend(order = 1),
         color  = guide_legend(order = 1))
#*****************

>>>>

```{r Density-plot, fig.height=4, fig.width=6.47}
I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity)) + 
  geom_histogram(data = observed, aes(y = ..density.., x = I2, fill = Heterogeneity), bins = 100, alpha = 0.6)   +
  stat_density(geom="line", position="identity", #we use stat_density instead of geom_density to get only the density lines (and no fill)
               aes(linetype = Heterogeneity, color = Heterogeneity), size = 0.75)+ 
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
  scale_fill_manual(name = NULL, #drop legend title so that can place directly under other legend
                    values = "#666666", #fill color
                    breaks = "Observed",
                    labels = "     Observed") + #space before Observed to align label with other labels since this guide has a different width to the others (see last line)
  scale_color_manual(values = c("#D95F02", "#E6AB02", "#1B9E77","#E7298A"), #fill colors
                     breaks = c("Zero", "Small", "Medium", "Large"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
  theme(legend.position = c(0.85, 0.71), #placement of legend
        legend.spacing = unit(-0.4, "cm"), #move the two legends close to each other to seem like one
        legend.key.width = unit(0.8, "cm"), #set default keywidth wider, so we can distinguis linetypes dashed and dotdash
        legend.background = element_blank(), #remove legend background so that we can put a shared box around the two legends
        legend.box.background = element_rect(colour = "black")) + #create the shared box
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(I)^2," index", sep = ""))) +
  guides(linetype = guide_legend(order = 1), #place linetype/color guides above fill guide
         color  = guide_legend(order = 1),
         fill = guide_legend(keywidth = unit(0.2, "cm"), #Make fill legend thinner to look like the histogram bars
                             direction = "horizontal")) #needed in combination with above
#*****************
